---
title: "LA County Propensity Score"
author: "Ryan Shields"
date: "March 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### Packages Required for Completion

- MatchIt is the main package we will be using for
- Matching is useful for similar functions as MatchIt
- MatchItSe is a method for evaluating standard error for matchit objects.
- dyplr is generally usefull and also controls lapply and looping functions for generating multiple plots.
- gpplot2 for plotting graphs
- ff for memory optimization for handling large files and reducing error of handling size.
- wfe for Difference in Difference
- RStata for writing Stata functions. 
```{r, message=FALSE, warning=FALSE}
library(Matching)
library(MatchIt)
library(MatchItSE)
library(dplyr)
library(ggplot2)
library(ff)
library(wfe)
library(RStata)
library(twang)
```

# Read in DataFile and Data Cleaning

### Load in CSV

Grab the output of data from the following GITHUB Code:
```{r, message=FALSE, warning=FALSE}
setwd("C:/users/DS049709/Desktop")

Target<- read.csv("LAC Managed HealthNet 90.csv")
Control<- read.csv("LAC NM HealthNet 90.csv")

#Target<- read.csv("LAC_CA_M_HEALTHNET_EXCLUDED.csv")
#Control<- read.csv("LAC_CA_NM_HEALTHNET_EXCLUDED.csv")

#Target<- read.csv("LAC_CA Feb_1_M.csv")
#Control<- read.csv("LAC_CA Feb_1_NM.csv")

#Target<- read.csv("LAC_CA Past_Managed_Encounter.csv")
#Control<- read.csv("LAC_CA Past_NM_Encounter.csv")

#Target<- read.csv("LAC_CA Past_Managed.csv")
#Control<- read.csv("LAC_CA Past_NM.csv")

#Target<- read.csv("LAC_Target_Population.csv")
#Control<- read.csv("LAC_Control_Population.csv")
```

# Data Cleaning

Currently more than one case can be managed. Get the first case for the non-managed empi's and the first managed case for the managed population.
```{r}
#Target Population First Case
Target.agg <- aggregate(managed_case ~ empi_id, Target, min)
Target_One_Case <- merge(Target.agg, Target)

#Control Population First Case
Control.agg <- aggregate(managed_case ~ empi_id, Control, min)
Control_One_Case <- merge(Control.agg, Control)

#Add managed Variable
Target_One_Case$managed <- as.integer(1)
Control_One_Case$managed <- as.integer(0)

#Union
Propensity <- union(Target_One_Case, Control_One_Case)
```

Fix the issue with individuals being able to have a defined and undefined race by recoding Race
```{r}
Propensity$Race_Sum <- rowSums(Propensity[,c("American_Indian", "Asian", "Black", "Caucasian", "Hispanic", "Pacific_Islander")])

df <- within(Propensity, Unknown[Unknown == 1 & Race_Sum == 1] <- 0)
```

Issue with 5 more lines than expected, 2 with gender issues, one with race: Turns out to be duplicate marital statuses. Re-run if you think you may have more than 1 line per empi_id
```{r}
#Check to see if unique empi's is less than total values in df
n_occur <- data.frame(table(df$empi_id))
```

Use Dplyer Function to get of by maxing the marital status and value. 
```{r}
# Use Dplyer Function to get one line per empi by maxing the marital status and value. 
df <- df %>% group_by(episode_of_care_id) %>% top_n(1, Marital_Status)
df <- df %>% group_by(episode_of_care_id) %>% top_n(1, gender_display)

#Issue with one row seperate lines in Caucasian and Hispanic (Prioritize minority race)
df <- df %>% group_by(episode_of_care_id) %>% top_n(1, Hispanic)

#Validate, make sure that df has the same number of observations as n_occur now. 
```

Reduce Data Frame
```{r, message=FALSE, warning=FALSE}
# Only Grab Rows that are required for Propensity score and D-I-D
prop <- df[c(37,1,4,5,6,7,8,9,10,11,12,13,20,26,27,28,29,30,31,32,33,34,35,36)]
test <- df[c(37,4,5,6,7,8,9,10,11,12,13,20,26,27,28,29,30,31,32,33,34,35,36)]

# Replace Missing Values With 0's, you cannot pace null values into a matchIt object
prop[is.na(prop)] <- 0
test[is.na(test)] <- 0

write.csv(prop, file = "C:/users/DS049709/Desktop/Prop.csv")
```

### Correlation Matrix
```{r, message=FALSE, warning=FALSE}
cor_mat <-test
cor_mat <- setNames(cor_mat, c("managed","age","Marital_Status","gender_display","American_Indian","Asian","Black","Caucasian","Hispanic","Pacific_Islander","Unknown","Identified_Algorithm","chronic_condition_total","physical_condition_present","mental_condition_present","Pre_Emergency","Pre_Outpatient","Pre_Inpatient","Pre_Observation","Post_Emergency","Post_Outpatient","Post_Inpatient","Post_Observation"))


mc_data <- cor_mat[,1:length(cor_mat)]
round(cor(mc_data),2)
round(cov(mc_data),2)
```

# Initial Statistics 

### Mean & Std.Error of Total Score
```{r}
prop.test <- na.omit(prop) #Omit Null Values

prop.test %>%
  group_by(managed) %>%
  summarise(n_patients = n(),
            mean_score = mean(chronic_condition_total),
            std_error = sd(chronic_condition_total) / sqrt(n_patients))
```

### Create a subset of group
Create a subgroup that contains every field but managed so we can generate inital covariates (T-tests) for each of the variables between managed and not managed. 
```{r}
prop_cov <-prop[,c(-1)]
```

### Inital Covariates for all of my variables selected above
A looping function that prints Welch's T-tests for all every variable.
```{r, warning= FALSE}
lapply(test[-1], function(x) t.test(x ~ test$managed))
```


### Logit Model of managed Against every other variable for significant variables.

We can estimate the propensity score by running a logit regression model. Outcome variable has to be binary indicating a treatment status. You include covariates that are realted to treatement assignment and outcomes. I've removed variables above that I did not wish to include and use all the remaining. 
```{r, message=FALSE, warning=FALSE}
m_prop <- glm(managed ~ ., family = binomial(), data = test)
summary(m_prop)
```
### Region of Common Support

Historgrams of the esimtated propensity scores by target and controlled groups. 
```{r}
#Using this model to calculate propensity scores for each care managmement patients.
prop_df <- data.frame(pr_score = predict(m_prop, type = "response"),
                     managed = m_prop$model$managed)

labs <- paste("Were you managed:", c("managed", "Not managed"))

prop_df %>%
  mutate(managed = ifelse(managed == 1, labs[1], labs[2])) %>%
  ggplot(aes(x = pr_score)) +
  geom_histogram(color = "white") +
  facet_wrap(~managed) +
  xlab("Probability of Being managed") +
  theme_bw()
```

# Matching

### MatchIt

Match managed and not managed population by Nearest Neighbors methods. This will be our base mode. The summary of this model can give of something information on how good of a job we did at Matching. 
```{r}
mod_match <- matchit(managed ~ age + Marital_Status + gender_display + American_Indian + Asian + Black + Caucasian + Hispanic + Pacific_Islander + Unknown + Identified_Algorithm + chronic_condition_total + physical_condition_present + mental_condition_present + Pre_Emergency + Pre_Outpatient + Pre_Inpatient + Pre_Observation + Post_Emergency + Post_Outpatient + Post_Inpatient + Post_Observation, method = "nearest", data = prop)

#summary(mod_match)
```



### Plot matching

Method of visualizing results of match algorithm
```{r}
plot(mod_match)
```
### Turn MatchIt object into a dataframe

```{r}
prop_m <- match.data(mod_match)
dim(prop_m)
```

### Use a smoother plot

These plots are used to estimate the mean of each covariates by each treatment status at the value of each propensity score. 6 plots at a time to not overcrowd. The better the match the closer the plots will have to near equal means. 
```{r}
fn_bal <- function(prop, variable) {
  prop$variable <- prop[, variable]
  if (variable == 'w3income') prop$variable <- prop$variable / 10^3
  prop$managed <- as.factor(prop$managed)
  support <- c(min(prop$variable), max(prop$variable))
  ggplot(prop, aes(x = distance, y = variable, color = managed)) +
    geom_point(alpha = 0.2, size = 1.3) +
    geom_smooth(method = "loess", se = F) +
    xlab("Propensity score") +
    ylab(variable) +
    theme_bw() +
    ylim(support)
}

library(gridExtra)
grid.arrange(
   fn_bal(prop_m, "Asian"),
   fn_bal(prop_m, "Hispanic") + theme(legend.position = "none"),
   fn_bal(prop_m, "Caucasian"),
   fn_bal(prop_m, "American_Indian") + theme(legend.position = "none"),
   fn_bal(prop_m, "Black"),
   fn_bal(prop_m, "Pacific_Islander"),
   nrow = 3, widths = c(1, 0.8)
)

```

B) Actually plotting. 

```{r}
library(gridExtra)
grid.arrange(
  fn_bal(prop_m, "gender_display"),
  fn_bal(prop_m, "Marital_Status"),
  fn_bal(prop_m, "age"),
  fn_bal(prop_m, "Identified_Algorithm"),
  fn_bal(prop_m, "chronic_condition_total"),
  fn_bal(prop_m, "physical_condition_present"),
  fn_bal(prop_m, "mental_condition_present"),
  nrow = 4, widths = c(1, 0.85)
)
```

### Compare our covariate t.tests. 

Out inital T-tests can be seen in the Results dataframe. Compare them side by side. We can see we did a good job at achieving balance, although not perfect for all covariates. 
```{r}
all_means <- test %>%
  group_by(managed) %>%
  summarise_all(funs(mean))

all_means
```

### Measuring the Absolute Standardized Differences in Error
```{r}
error <- abs(all_means - as.list(all_means[1, ]))
error <- error[-1,-c(1,24,25)]
rowMeans(error)
rowSums(error)
```

# Second Attempt with a custom model

### Model 2: Optimal My Model
```{r}
mod_match2 <- matchit(managed ~ age + Marital_Status + gender_display + American_Indian + Asian + Black + Caucasian + Hispanic + Pacific_Islander + Unknown + Identified_Algorithm + chronic_condition_total + physical_condition_present + mental_condition_present + Pre_Emergency + Pre_Outpatient + Pre_Inpatient + Pre_Observation, method = "nearest", distance = 'probit', discard = 'both', restimate = TRUE, data = prop)
```

```{r}
prop_m2 <- match.data(mod_match2)
prop_m2 <- prop_m2[c(1,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26)]

summary(mod_match2,standardize = TRUE)
```

```{r}
# Exposing matched pairs, like if Jeff wants it or something.....
a<-data.frame(prop$empi_id,mod_match2$treat,mod_match2$weights)
colnames(a)<-c("id_num","trt","weights")

b<-as.data.frame(mod_match2$match.matrix)
colnames(b)<-c("matched_unit")

b$matched_unit<-as.numeric(as.character(b$matched_unit))
b$treated_unit<-as.numeric(rownames(b))

c<-b[!is.na(b$matched_unit),]
c$match_num<-1:dim(c)[1]

a[c$matched_unit,4]<-c$match_num
a[c$treated_unit,4]<-c$match_num
colnames(a)[4]<-"match_num"


a<- a[!is.na(a$match_num),]
d <- a[order(a$match_num),] 

write.csv(d, file = "C:/users/DS049709/Desktop/Matches.csv")

```


```{r}
all_means2 <- prop_m2 %>%
  group_by(managed) %>%
  summarise_all(funs(mean))

all_means2
```

```{r}
error2 <- abs(all_means2 - as.list(all_means2[1, ]))
error2 <- error2[-1,-c(1,24,25,26)]
rowMeans(error2)
rowSums(error2)
```

###########

```{r}
head(summary(mod_match2, interactions = FALSE , standardize = TRUE, addlvariables = TRUE))
```

### Measuring Standard Error
```{r}
m.out <- matchit(managed ~ age + Marital_Status + gender_display + American_Indian + Asian + Black + Caucasian + Hispanic + Pacific_Islander + Unknown + Identified_Algorithm + chronic_condition_total + physical_condition_present + mental_condition_present + Pre_Emergency + Pre_Outpatient + Pre_Inpatient + Pre_Observation, method = "nearest", verbose = TRUE, distance = 'linear.logit', distance.options = list(maxit = 10000), discard = "treat", m.order ="largest",  data = prop_m2)

zelig_se(obj = m.out, Y = prop_m$chronic_condition_total)

lechner_se(obj = m.out, Y = prop_m$chronic_condition_total)
```

```{r}
library(gridExtra)
grid.arrange(
  fn_bal(prop_m2, "gender_display"),
  fn_bal(prop_m2, "Identified_Algorithm"),
  fn_bal(prop_m2, "Pre_Observation"),
  fn_bal(prop_m2, "Pre_Inpatient"),
  fn_bal(prop_m2, "Pre_Outpatient"),
  fn_bal(prop_m2, "chronic_condition_total"),
  nrow = 3, widths = c(1, 0.85)
)
```
# Jitter Plot
```{r}
plot(mod_match2, type = 'jitter', interactive = FALSE)
```

```{r}
plot(mod_match2)
```

#Pre-Intervention
```{r}
ag_mean <- aggregate(. ~ managed, test, function(x) c(mean = mean(x)))
ag_mean$Function <- "Mean"
ag_sd <- aggregate(. ~ managed, test, function(x) c(sd = sd(x)))
ag_sd$Function <- "SD"
total <- rbind(ag_mean, ag_sd)
total
```
### Post-Intervention
```{r}
ag_mean <- aggregate(. ~ managed, prop_m2, function(x) c(mean = mean(x)))
ag_mean$Function <- "Mean"
ag_sd <- aggregate(. ~ managed, prop_m2, function(x) c(sd = sd(x)))
ag_sd$Function <- "SD"
total_2 <- rbind(ag_mean, ag_sd)
total_2
```

```{r}
write.csv(prop_m2, file = "C:/users/DS049709/Desktop/MyData.csv")
```

# Difference in Difference

### Transform and merge data frame
```{r}
did_m <- test[c(1,12,13,14,15,16,17,18,19,20,21,22,23)]
```

### Create 5 Algorithms 
```{r}
did_hra <- subset(prop_m2, Identified_Algorithm =='1')
did_mat <- subset(prop_m2, Identified_Algorithm =='2')
did_ped <- subset(prop_m2, Identified_Algorithm =='3')
did_tran <- subset(prop_m2, Identified_Algorithm =='4')
did_util <-subset(prop_m2, Identified_Algorithm =='5')
did_manual <-subset(prop_m2, Identified_Algorithm =='0')
```

### Differences in Differences for Pre/Post Utilization Visits

These units can be dicussed in like terms. Meaning number of visits an average pre or post person needs. 
```{r}
#Outpatient Visit
(mean(prop_m2$Post_Outpatient[prop_m2$managed==1]) - mean(prop_m2$Pre_Outpatient[prop_m2$managed==1])) - (mean(prop_m2$Post_Outpatient[prop_m2$managed==0]) - mean(prop_m2$Pre_Outpatient[prop_m2$managed==0]))

#Inpatient Visit 
(mean(prop_m2$Post_Inpatient[prop_m2$managed==1]) - mean(prop_m2$Pre_Inpatient[prop_m2$managed==1])) - (mean(prop_m2$Post_Inpatient[prop_m2$managed==0]) - mean(prop_m2$Pre_Inpatient[prop_m2$managed==0]))

#Observation Visit
(mean(prop_m2$Post_Observation[prop_m2$managed==1]) - mean(prop_m2$Pre_Observation[prop_m2$managed==1])) - (mean(prop_m2$Post_Observation[prop_m2$managed==0]) - mean(prop_m2$Pre_Observation[prop_m2$managed==0]))

#Emergency
(mean(prop_m2$Post_Emergency[prop_m2$managed==1]) - mean(prop_m2$Pre_Emergency[prop_m2$managed==1])) - (mean(prop_m2$Post_Emergency[prop_m2$managed==0]) - mean(prop_m2$Pre_Emergency[prop_m2$managed==0]))
```

### By Algorithm
#High-Risk Adult and Senior

```{r}
#Outpatient Visit
(mean(did_hra$Post_Outpatient[did_hra$managed==1]) - mean(did_hra$Pre_Outpatient[did_hra$managed==1])) - (mean(did_hra$Post_Outpatient[did_hra$managed==0]) - mean(did_hra$Pre_Outpatient[did_hra$managed==0]))

#Inpatient Visit 
(mean(did_hra$Post_Inpatient[did_hra$managed==1]) - mean(did_hra$Pre_Inpatient[did_hra$managed==1])) - (mean(did_hra$Post_Inpatient[did_hra$managed==0]) - mean(did_hra$Pre_Inpatient[did_hra$managed==0]))

#Observation Visit
(mean(did_hra$Post_Observation[did_hra$managed==1]) - mean(did_hra$Pre_Observation[did_hra$managed==1])) - (mean(did_hra$Post_Observation[did_hra$managed==0]) - mean(did_hra$Pre_Observation[did_hra$managed==0]))

#Emergency
(mean(did_hra$Post_Emergency[did_hra$managed==1]) - mean(did_hra$Pre_Emergency[did_hra$managed==1])) - (mean(did_hra$Post_Emergency[did_hra$managed==0]) - mean(did_hra$Pre_Emergency[did_hra$managed==0]))
```

# High-Risk Maternity
```{r}
#Outpatient Visit
(mean(did_mat$Post_Outpatient[did_mat$managed==1]) - mean(did_mat$Pre_Outpatient[did_mat$managed==1])) - (mean(did_mat$Post_Outpatient[did_mat$managed==0]) - mean(did_mat$Pre_Outpatient[did_mat$managed==0]))

#Inpatient Visit 
(mean(did_mat$Post_Inpatient[did_mat$managed==1]) - mean(did_mat$Pre_Inpatient[did_mat$managed==1])) - (mean(did_mat$Post_Inpatient[did_mat$managed==0]) - mean(did_mat$Pre_Inpatient[did_mat$managed==0]))

#Observation Visit
(mean(did_mat$Post_Observation[did_mat$managed==1]) - mean(did_mat$Pre_Observation[did_mat$managed==1])) - (mean(did_mat$Post_Observation[did_mat$managed==0]) - mean(did_mat$Pre_Observation[did_mat$managed==0]))

#Emergency
(mean(did_mat$Post_Emergency[did_mat$managed==1]) - mean(did_mat$Pre_Emergency[did_mat$managed==1])) - (mean(did_mat$Post_Emergency[did_mat$managed==0]) - mean(did_mat$Pre_Emergency[did_mat$managed==0]))
```

#High-Risk Peds
```{r}
#Outpatient Visit
(mean(did_ped$Post_Outpatient[did_ped$managed==1]) - mean(did_ped$Pre_Outpatient[did_ped$managed==1])) - (mean(did_ped$Post_Outpatient[did_ped$managed==0]) - mean(did_ped$Pre_Outpatient[did_ped$managed==0]))

#Inpatient Visit 
(mean(did_ped$Post_Inpatient[did_ped$managed==1]) - mean(did_ped$Pre_Inpatient[did_ped$managed==1])) - (mean(did_ped$Post_Inpatient[did_ped$managed==0]) - mean(did_ped$Pre_Inpatient[did_ped$managed==0]))

#Observation Visit
(mean(did_ped$Post_Observation[did_ped$managed==1]) - mean(did_ped$Pre_Observation[did_ped$managed==1])) - (mean(did_ped$Post_Observation[did_ped$managed==0]) - mean(did_ped$Pre_Observation[did_ped$managed==0]))

#Emergency
(mean(did_ped$Post_Emergency[did_ped$managed==1]) - mean(did_ped$Pre_Emergency[did_ped$managed==1])) - (mean(did_ped$Post_Emergency[did_ped$managed==0]) - mean(did_ped$Pre_Emergency[did_ped$managed==0]))
```

#Transitions of Care
```{r}
#Outpatient Visit
(mean(did_tran$Post_Outpatient[did_tran$managed==1]) - mean(did_tran$Pre_Outpatient[did_tran$managed==1])) - (mean(did_tran$Post_Outpatient[did_tran$managed==0]) - mean(did_tran$Pre_Outpatient[did_tran$managed==0]))

#Inpatient Visit 
(mean(did_tran$Post_Inpatient[did_tran$managed==1]) - mean(did_tran$Pre_Inpatient[did_tran$managed==1])) - (mean(did_tran$Post_Inpatient[did_tran$managed==0]) - mean(did_tran$Pre_Inpatient[did_tran$managed==0]))

#Observation Visit
(mean(did_tran$Post_Observation[did_tran$managed==1]) - mean(did_tran$Pre_Observation[did_tran$managed==1])) - (mean(did_tran$Post_Observation[did_tran$managed==0]) - mean(did_tran$Pre_Observation[did_tran$managed==0]))

#Emergency
(mean(did_tran$Post_Emergency[did_tran$managed==1]) - mean(did_tran$Pre_Emergency[did_tran$managed==1])) - (mean(did_tran$Post_Emergency[did_tran$managed==0]) - mean(did_tran$Pre_Emergency[did_tran$managed==0]))
```

#Utilization Coordination
```{r}
#Outpatient Visit
(mean(did_util$Post_Outpatient[did_util$managed==1]) - mean(did_util$Pre_Outpatient[did_util$managed==1])) - (mean(did_util$Post_Outpatient[did_util$managed==0]) - mean(did_util$Pre_Outpatient[did_util$managed==0]))

#Inpatient Visit 
(mean(did_util$Post_Inpatient[did_util$managed==1]) - mean(did_util$Pre_Inpatient[did_util$managed==1])) - (mean(did_util$Post_Inpatient[did_util$managed==0]) - mean(did_util$Pre_Inpatient[did_util$managed==0]))

#Observation Visit
(mean(did_util$Post_Observation[did_util$managed==1]) - mean(did_util$Pre_Observation[did_util$managed==1])) - (mean(did_util$Post_Observation[did_util$managed==0]) - mean(did_util$Pre_Observation[did_util$managed==0]))

#Emergency
(mean(did_util$Post_Emergency[did_util$managed==1]) - mean(did_util$Pre_Emergency[did_util$managed==1])) - (mean(did_util$Post_Emergency[did_util$managed==0]) - mean(did_util$Pre_Emergency[did_util$managed==0]))
```

#Manual
```{r}
#Outpatient Visit
(mean(did_manual$Post_Outpatient[did_manual$managed==1]) - mean(did_manual$Pre_Outpatient[did_manual$managed==1])) - (mean(did_manual$Post_Outpatient[did_manual$managed==0]) - mean(did_manual$Pre_Outpatient[did_manual$managed==0]))

#Inpatient Visit 
(mean(did_manual$Post_Inpatient[did_manual$managed==1]) - mean(did_manual$Pre_Inpatient[did_manual$managed==1])) - (mean(did_manual$Post_Inpatient[did_manual$managed==0]) - mean(did_manual$Pre_Inpatient[did_manual$managed==0]))

#Observation Visit
(mean(did_manual$Post_Observation[did_manual$managed==1]) - mean(did_manual$Pre_Observation[did_manual$managed==1])) - (mean(did_manual$Post_Observation[did_manual$managed==0]) - mean(did_manual$Pre_Observation[did_manual$managed==0]))

#Emergency
(mean(did_manual$Post_Emergency[did_manual$managed==1]) - mean(did_manual$Pre_Emergency[did_manual$managed==1])) - (mean(did_manual$Post_Emergency[did_manual$managed==0]) - mean(did_manual$Pre_Emergency[did_manual$managed==0]))
```

#Clean up data to Re-arrange
```{r}
did_pre <- did_m[c(1,2,6,7,8,9)]
did_pre$time <- 0
did_post<- did_m[c(1,2,10,11,12,13)]
did_post$time <- 1

#Rename a bunch of columns in order to Rbind
colnames(did_post)[colnames(did_post)=="Post_Outpatient"] <- "Outpatient"
colnames(did_post)[colnames(did_post)=="Post_Emergency"] <- "Emergency"
colnames(did_post)[colnames(did_post)=="Post_Inpatient"] <- "Inpatient"
colnames(did_post)[colnames(did_post)=="Post_Observation"] <- "Observation"
colnames(did_post)[colnames(did_post)=="managedNA"] <- "managed"

colnames(did_pre)[colnames(did_pre)=="Pre_Outpatient"] <- "Outpatient"
colnames(did_pre)[colnames(did_pre)=="Pre_Emergency"] <- "Emergency"
colnames(did_pre)[colnames(did_pre)=="Pre_Inpatient"] <- "Inpatient"
colnames(did_pre)[colnames(did_pre)=="Pre_Observation"] <- "Observation"
colnames(did_pre)[colnames(did_pre)=="managedNA"] <- "managed"

did_total <- rbind(did_pre,did_post)
```

```{r}
HRA <- did_total[did_total$Identified_Algorithm == 1, ]
MAT <- did_total[did_total$Identified_Algorithm == 2, ]
PED <- did_total[did_total$Identified_Algorithm == 3, ]
TRAN <- did_total[did_total$Identified_Algorithm == 4, ]
UTIL <- did_total[did_total$Identified_Algorithm == 5, ]
MAN <- did_total[did_total$Identified_Algorithm == 0, ]
```

# Linear Regression
```{r}
did_In <- lm(Inpatient ~ time + managed + time*managed, data = MAN)
summary(did_In)
```


```{r}
did_Out <- lm(Outpatient ~ time + managed + time*managed, data = UTIL)
summary(did_Out)
```

```{r}
did_Emer <- lm(Emergency ~ time + managed + time*managed, data = MAN)
summary(did_Emer)
```

```{r}
did_Out <- lm(Outpatient ~ time + managed + time*managed, data = did_total)
summary(did_Out)
```